### 2015-05-14 whoop.tex
fix

\begin{figure}[t]
\begin{lstlisting}
const struct file_operations nvram_fops = {
  .llseek = nvram_llseek,
  .read = read_nvram,
  .write = write_nvram,
  .unlocked_ioctl = nvram_unlocked_ioctl,
};
\end{lstlisting}
\caption{Entry points definitions in the generic\_nvram driver}
\label{fig:entrypoints}
\end{figure}

>>>>

\begin{figure}[t]
\begin{lstlisting}
const struct file_operations nvram_fops = {
  .llseek = nvram_llseek,
  .read = read_nvram,
  .write = write_nvram,
  .unlocked_ioctl = nvram_unlocked_ioctl
};
\end{lstlisting}
\caption{Entry points definitions in the generic\_nvram driver}
\label{fig:entrypoints}
\end{figure}
